Coupling microsimulation models with land-use transport models

### 2019-01-18 main.tex
Update on Overleaf.

A strong need of multi-scalar models to be applied to sustainable policy making is already shaping the construction of the next generation of territorial models \cite{Rozenblat2018}. Indeed, the coupling of complementary modeling approaches to the same systems is coined by \cite{banos2013pour} as an essential step forward in social simulation to be able to better tackle the complexity of such systems. The modeling activity must furthermore be highly integrated with other knowledge domains \cite{raimbault2017applied}, in particular empirical and theoretical approaches, to foster the production of applicable complex knowledge.

>>>>

A strong need of multi-scalar models to be applied to sustainable urban policy making is already shaping the construction of the next generation of territorial models \cite{Rozenblat2018}. Indeed, the coupling of complementary modeling approaches to the same systems is coined by \cite{banos2013pour} as an essential step forward in social simulation to be able to better tackle the complexity of such systems. The modeling activity must furthermore be highly integrated with other knowledge domains \cite{raimbault2017applied}, in particular empirical and theoretical approaches, to foster the production of applicable complex knowledge.
